A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-04-08 faculty.tex
updates

\subsection{Letters}
This is a huge part of the tenure package. You will need to ask for letters from senior people in your area.  Someone who can vouch for your research, teaching, and services.

You will need 4-6 letters, however you will not be the one asking for these letters, but your department will. However you can suggest who to ask. Typically, there will be two list of letter writers: one list consists of people suggested by you and the other list has people suggested by the department (e.g., people who work in your field in your dept).

Originally I asked several senior people in my area to write letters for me. Then I found out that there is a rule at GMU that I cannot ask people whom have collaboration with me in the last 7 years!!! That essentially make most of my letter writers invalid.  Moreover, GMU (and likely most other universities) prefer letter writers not from my list (because people on my list are likely to be biased), and has a rule that at least 60\% of the letter writers must be from the department's list. Also, there's a good chance that a letter writer will decline the invitation, so there should be more than 4-6 names in the lists.

After talking to various people in my dept and outside, I decide to put just 2 names in my list and let the department decides the rest. I even thought about leaving my list empty but then that seems to be too weird and I don't want to give the impression that I don't have any friends in the world.  Essentially this means that likely none or 1 of

The reason is because I feel I don't have too many "enemies" out there that would write bad things about me.  Those that don't know me well will likely just decline the letter invitation.  Turned out to be a good decision because later I learn that all my letters wrote very positive things about me.  I will never know who wrote the letters, but I am very grateful to them.

>>>>

\subsection{Letters}
This is a huge part of your tenure package.  You will need to ask for letters from senior people in your area.  Someone who can vouch for your research, teaching, and services.
You will need 4-6 letters. However, you will not be the one asking for these letters, but your department will. You can suggest who to ask.

Typically, there are two lists of letter writers: one consisting of people suggested by you and the other consisting of people suggested by the department (e.g., people who work in your field in your dept). There can also be another list, the ``blacklist'' where you list people that you don't want to write letters for you.

Originally I asked several senior people to write my letters. Then I found out that there is a rule at GMU that I cannot ask people whom have collaboration with me in the last 7 years!!! That invalidates most of my letter writers.  Moreover, GMU (and likely most other universities) would prefer writers not from my list (because people on my list are likely to be biased), and has a rule that at least 60\% of the letter writers must be from the department's list. Moreover, there's a good chance that a letter writer will decline the invitation, so there should be more names.

After talking to various people in my dept and outside, I decide to put just 2 names in my list (0 on blacklist) and let the department decides the rest. I also thought about leaving my list empty but then that seems to be too weird, and I don't want to give the impression that I don't have any friends in the world.
The reason is that I feel I don't have too many "enemies" out there that would write bad things about me.  Those that don't know me well will likely just decline the letter invitation. Turned out to be a good decision because in the end the department selected 1 of the 2 names on my list and 4 more names from the department's list. Moreover, it looks like no one declines so my letter writers are all set fairly quickly in the process.  All of my letters were good and give many positive comments about me as summarized in my evaluation letter (sent to me after the tenure decision).  I will never know who wrote the letters, but I am very grateful to them.
